---
fontsize: 12pt
geometry: "driver=luatex,paper=letterpaper,hmargin=2.0cm,vmargin=1.5cm,headsep=0.75cm,headheight=0.75cm,includeheadfoot"
output: 
  pdf_document: 
    includes:
      in_header: header.tex
    latex_engine: lualatex
    keep_tex: true
    extra_dependencies: ['enumitem', 'amsmath', 'amssymb']
---
\begin{titlepage}
        \centering
        \mbox{}
        \vfill
        {\Huge Handwritten Digit Recognition\\
        with Neural Networks\par}
        \vspace{2\baselineskip}
        {\large Tanner Giddings\\
        Mairi Hallman\\
        Victor Matyiku\\
        Mitchell Whalen\par}
        \vspace{4\baselineskip}
        {Statistical Machine Learning\\
        Winter 2024\par}
        \vspace{\baselineskip}
        {Universit\symbol{"00E9} d'Ottawa\\
        University of Ottawa\par}
        \vspace{2\baselineskip}
        \today
\end{titlepage}
```{r 'import-packages', echo = FALSE}
library(tinytex)
library(reticulate)
```
```{r 'chunk-settings', echo = FALSE}
#knitr::opts_chunk$set()
```
```{python 'import-data'}
import scipy, numpy
M = scipy.io.loadmat("data/mnist_all.mat")
batches = list(M)
for name in batches:
  if "_" in name:
    batches.remove(name)
batches.remove("__version__")
for name in batches:
  M[name] = numpy.divide(M[name], 255.0)
```